Interlocks Mitigate Information Cascades in Large-Scale Social Learning

### 2024-10-28 manuscript.tex
Updates from Overleaf

%% These commands are for a PROCEEDINGS abstract or paper.
\acmConference[CSCW '25]{Make sure to enter the correct
  conference title from your rights confirmation emai}{Nov 0,
  2025}{City, Country}
\acmISBN{978-1-4503-XXXX-X/18/06}

@@

\subsection{Agent-Based Modeling\label{subsec:abm}}

@@

We draw attention to the above distinction because of a subtle, but very important point.
As discussed in Section \ref{subsec:social} there are two related but separate approaches to participatory governance.

@@

The NK Model bridges these two approaches.
It asks: given a set of subjective preferences,
what is the objective quality of a particular outcome?

\subsubsection{Properties of the NK Model}

\subsubsection{Assmptions of the NK Model}

>>>>

%% These commands are for a PROCEEDINGS abstract or paper.
\acmConference[CSCW '25]{Make sure to enter the correct
  conference title from your rights confirmation emai}{Oct 18--22
  2025}{Bergen, Norway}
\acmISBN{978-1-4503-XXXX-X/18/06}

@@

\subsection{Agent-Based Modeling\label{subsec:abm}}
Our Agent-Based Model (ABM) closely follows previous ABM work on social learning
\cite{lazer_network_2007, barkoczi_social_2016, gomez_clustering_2019}.
The ABM consists of a large collection of {\em agents}:
simulated entities, each with their own private information and the ability to update that information based on interactions with other agents.
In our case, the agents are intended to represent
individual participants in a participatory decision-making
process.
The exact behavior of the agents is determined by three factors:
\begin{description}
\item[Objective Function]
At the beginning of each ABM run, an objective function $Q(s)$ is defined.
The goal of the agents is to find an $s$ that maximizes
$Q(s)$.
\item[Social Network]
The social network provides links between some pairs of agents and not others.
These links allow neighboring agents to interact with each other and share information.
\item[Social Learning Strategy]
The social learning strategy is a simple set of rules the agents use to interact with their neighbors and update their belief about the best value of $s$.
\end{description}

At the beginning of a simulation run, each agent is initialized with a random $s$.
The run proceeds in discrete time steps.
At each time steps, each agent interacts with each of its neighbors according to its strategy and
updates its belief.
After a fixed number of time steps, the run ends.
Ideally, the number of time steps is large enough that
the agents' beliefs have reached a stable state.
Different agents may still have different beliefs,
but at this point the distributions of beliefs and the potential outcomes of votes can be analyzed.
This process is repeated for many runs,
each with a new set of initial conditions and objective $Q(s)$.
By performing many runs, statistical differences between different networks and/or strategies can be identified.

@@

We draw attention to the above distinction because of a subtle, but very important point.
As discussed in Section \ref{subsec:social} there are two related but separate approaches to participatory governance.
One, to advocate for a preferred outcome based on preferences;
the other, to determine which outcome would best satisfy everyone's preferences.
The NK Model bridges these two approaches.
It asks: given a random set of subjective preferences,
what is the objective quality of a particular outcome?

\subsubsection{Properties of the NK Model}
The real-world applicability of our findings will depend on how well a real-world system agrees with the assumptions of our model.
We enumerate key assumptions and properties below.
\begin{description}
\item[Discrete solution space]
The NK model solution space consists of discrete states.
This space best represents a set of yes/no questions.
However, the NK model can also be applied to any solution space that can be approximated by a discrete set of solutions, for example, by dividing a continuous range into bins.
\item[Large solution space]
There are $2^N$ possible solutions for any particular instance of the NK model.
The number of solutions grows exponentially with the number of bits in $s$.
The NK model is thus well-suited to representing problems with far more potential solutions than could ever be evaluated.
For example, for N=33, there would be more potential solutions than humans alive on Earth (at time of writing).
\item[Rugged solution space]
Often called a ``rugged landscape,'' the NK model has many local maxima and minima,
often described as ``hills'' and ``valleys.''
A simple hill-climbing search by changing one solution bit at a time will lead to a local maximum,
but there is no way to know if a better solution exists, other than searching for it.
This is a common (if frustrating) feature of real-world problems.
\item[Tunably rugged]
In addition to being rugged, the ruggedness of the NK model can be ``tuned'' by changing the $K$ parameter.
For a value of $K=0$, each solution bit can be optimized independently, and there is a single local maximum.
For the maximum value of $K=N-1$,
the landscape is essentially random.
For intermediate values of $K$,
there are a large number of local maxima, but they are surrounded by ``basins of attraction'' which allow those maxima to be found from nearby solutions using hill-climbing.
These intermediate values are typically the ones used to mimic real-world rugged landscapes.
\item[NP-complete]
For $K \geq 3$, the problem of finding the global optimum of the NK model in general is NP-complete \cite{weinberger_np_1996}.
This means that the NK model is computationally equivalent to the hardest problems solvable by a computer,
and can thus model the complexity of any problem that is capable of being modeled computationally.
\end{description}

@@
